You have more money in your wallet. Does that mean you will spend extra on food?

### 2024-04-13 paper/paper.qmd
updates the test folder

Wages have been going up in the US for the past thirty years, which usually means people have more money to spend after taxes. This extra money, called disposable income, is what's left over after taxes are taken out of a person's income. It's an important thing to look at because it shows how much money people have to spend. Research shows that when people have more disposable income, they tend to spend more money [@friend1946relationship]. We're interested in how strong this connection is when it comes to one specific thing: food.

Food is something everyone needs to live. People might change what kinds of food they like over time, but everyone still needs to eat. In this project, we're looking at how closely linked disposable income is to how much people spend on food. This matters because if there's a strong connection, it suggests that when people make more money, they tend to spend more on basics like food. This could help predict how much people will spend on luxury items in the future. For instance, if we find a strong connection, it might mean that when people earn more, they spend a bigger chunk of their money on essentials like food, leaving less for luxury items.

Numerous studies, notably summarized by Ernst Engel's law, suggest that as income and family size increase, spending on food goes up, but the proportion of income spent on food decreases [@lewbel2008engel]. This means wealthier families tend to spend more on food, but it's a smaller part of their overall income. Taking inspiration from Engel's law, we want to see how food spending changes when we look at other spending categories instead of just income differences across families.

Additionally, most past studies used income as the predictor variable, but we're using disposable income because we think it gives a better idea of overall wealth. The estimand of this paper is the measure of how much food spending changes (in billions of USD) when disposable income increases by a billion USD.

>>>>

Over the past thirty years in the US, wages have consistently risen, while tax rates have remained relatively stable. This has resulted in people having more disposable income, which is the money left after taxes are deducted from one's income. Disposable income is crucial to consider as it reflects the actual amount of money available for spending. Studies indicate that when individuals have higher disposable income, they generally spend more [@friend1946relationship]. We are particularly interested in examining this relationship in the context of food.

Food is something everyone needs to live. People might change what kinds of food they like over time, but everyone still needs to eat. In this project, we're looking at how closely linked disposable income is to how much people spend on food. This matters because if there's a strong connection, it suggests that when people make more money, they tend to spend more on basic goods and services like food. Further, this could help predict how much people will spend on luxury items in the future. For instance, if we find a strong connection, it might mean that when people earn more, they spend a bigger chunk of their money on essentials like food, leaving less for luxury items.

Numerous studies, notably summarized by Ernst Engel's law, suggest that as income and family size increase, spending on food goes up. However, the proportion of income spent on food decreases [@lewbel2008engel]. This means wealthier families tend to spend more on food, but it is a smaller part of their overall income. Taking inspiration from Engel's law, we want to see how food spending changes when we account for other spending categories instead of just income differences across families. Additionally, most past studies used income as the predictor variable, but we're using disposable income because we think it gives a better idea of overall wealth. The estimand of this paper is the measure of how much food spending changes (in billions of USD) when disposable income increases by a billion USD.
